---
title: "ESM206 Lab 10"
author: "Anna Abelman"
date: "12/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(corrplot)
library(beepr)
library(praise)
library(stargazer)
library(sf)
library(gganimate)
library(transformr)

```

## Objectives:

- mutliple linear regression
- out first map with sf and ggplot


### 1. Multiple linear regression: SLO home prices

```{r}
homes <- read_csv("slo_homes.csv") %>% 
  clean_names()

beep(3)
praise()

praise("You are totally ${adjective}! Super ${EXCLAMATION}!")
```

```{r}
homes_sub <- homes %>% 
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande"))
```

Are there correlations between variables that we'd consider while trying to model home price?

```{r}
homes_cor <- cor(homes_sub[2:5])
homes_cor

corrplot(homes_cor,
         method = "ellipse",
         type = "upper")

```

is there any reason to think this is no a multi linear relationship?

```{r}
ggplot(data = homes_sub, aes(x = sq_ft, y = price))+
  geom_point()

ggplot(data = homes_sub, aes(x = bedrooms, y = price))+
  geom_point()
```

Let's start with a complete model (includes city, bedrooms, bathroom, sq_ft, and sale status):

```{r}
homes_lm <- lm(price ~ city + bedrooms + bathrooms + sq_ft + status, data = homes_sub)

summary(homes_lm)
# estimates are the coefficients in the linear equations for each variable
#reference levels would be city - Arroyo Grande and status - Foreclosure
# bedroom is an example of possible colinearity because it is decrease -161645 each time for a bedroom 
```
This model significantly predict the home price

Now let's try another version of the model:
- just using sq_ft as a measure of home size
```{r}
homes_lm2 <- lm(price ~ city + sq_ft + status, data = homes_sub)
summary(homes_lm2)

beep(6)
praise()

```

AIC:
```{r}
AIC(homes_lm)
AIC(homes_lm2)

# homes_lm is lower so it is the better model, however, it should be the least interesting part and conceptually should make the most sense
#does it make sense conceptually that bedrooms and bathrooms should increase or decrease the price of the house? the sq_ft measure is best to determine the price

#model 2 is the conceptually more sound 
```

### Now: check the assumptions for normality and homoscedasticity
- normality refers to the distribution of the residuals NOT THE DISTRIBUTION OF THE DATA

```{r}
plot(homes_lm2)

#1: actual residual values; are the variances constant or changing throughoout? --> looks like the assumption of constant variances of residuals (homoscedasticity) is OK
#2: qq plot - is there are linear relationship? --> straight line so normally distribution
# cook's distance: comparing leverage on a model

praise()
```

Make a nice regression table:
```{r, results = 'asis'}

stargazer(homes_lm2, type = "html")


```

Let's make some predictions for how price based on a new data frame from of home characteristics

Make sure that the variables we create for the new data match the variables that the model will be looking for to make new predictions.

```{r}
new_df <- data.frame(
  city = rep(c("San Luis Obispo", "Arroyo Grande", "Atascadero"), each = 10), 
  sq_ft = rep(seq(1000, 5000, length = 10)),
  status = "Regular"
)

```

Now: We'll make predictions for home rpice based on that new data:
```{r}
predict_df <- predict(homes_lm2, newdata = new_df)
predict_df

#bind together the new_df with the predictions:
full_data <- data.frame(new_df, predict_df)
full_data
```

Now plot in ggplot2:

```{r}
ggplot()+
  geom_point(data = homes_sub, aes(x = sq_ft, y = price, color = city, pch = city))+
  geom_line(data = full_data, aes(x = sq_ft, y = predict_df, color = city))+
  scale_color_manual(values = c("orange", "magenta", "black"))+
  theme_minimal()
```

### Our first map 
- great because: sticky geometries

```{r}
dams <- read_csv("ca_dams.csv") %>% 
  clean_names() %>% 
  drop_na(latitude) %>% 
  drop_na(longitude) %>% 
  drop_na(year_completed)
```

convert our data frame to an sf object using st_as_sf:
```{r}
dams_sf <- st_as_sf(dams, coords = c("longitude", "latitude"))
st_crs(dams_sf) <- 4326

plot(dams_sf)

```

Read in the California border polygon data:
```{r}
library(here)
ca_border <- read_sf(here::here("ca_state_border"), layer = "CA_State_TIGER2016")

plot(ca_border)
```

Now let's plot them together with ggplot2:
```{r}
ggplot()+
  geom_sf(data = dams_sf, color = "skyblue", size = 1, alpha = 0.4)

ggplot()+
  geom_sf(data = ca_border, color = "light gray", color = "black")+
  theme_void()


ggplot()+
  geom_sf(data = ca_border, color = "light gray", color = "black")+
  geom_sf(data = dams_sf, color = "skyblue", size = 1, alpha = 0.4)+
  theme_minimal()

```

Now let's animate it with gganimate

```{r}
ggplot()+
  geom_sf(data = ca_border, color = "light gray", color = "black")+
  geom_sf(data = dams_sf, color = "skyblue", size = 1, alpha = 0.4)+
  theme_void()+
  labs(title = 'Year: {round(frame_time, 0)}')+
  transition_time(year_completed)+
  shadow_mark()
```












